Pipeline systems and infrastructure for the efficient and open processing of Big neuroimaging Data

### 2018-02-25 paper.tex
openMOLE summary

    \section{OpenMOLE}
        \subsection{summary}
        \subsection{Pipeline description}
        \subsection{Pipeline execution}
        \subsection{Debugging and Provenance}
    \section{LONI}
    \section{Automatic Analysis}
    \section{Dipy, Make, Pydiper} 
    \section{Use of containers in Workflow engines} 
        \subsection{use of containers in nipype, psom, spm}

>>>>

    \section{OpenMOLE}
        \subsection{summary}
        OpenMOLE (Open MOdeL Experiment) is a domain agnostic pipelining
framework that focuses on simplifying workflow creation through its Domain
Specific Language (DSL) built on top of Scala. Through the use of its DSL, much
of the backend is abstracted from users. Similarly to other existing pipelining
frameworks, OpenMOLE enables parallelization through plugins, meaning that the
workflow need not be changed between different distribution environments.
Moreover, OpenMOLE supports the deployment of tasks or groups of tasks on different
computing environments.
Another key feature of OpenMOLE is that it attempts to address the
reproducibility issue through the integration of the CARE archiver. CARE allows
for the execution of command-line applications, written in any language, and
attempts to simulate the environment in which the application was designed on.
OpenMOLE also provides embedded methods for parameter exploration.

        \subsection{Pipeline description}
       An OpenMOLE workflow consists of tasks connected by transitions. Each
task contains details such as input, output and optional parameters, in addition
to embedding the application that will be applied to the data. Input values are
generally supplied by the dataflow through an entry point known as
\textit{Sources} and output values are returned to the
dataflow through \textit{Hooks}.

      Variables in OpenMOLE can be native types (e.g. int, string), files,
directories, any Java or Scala types, and user-defined types (i.e. Java or Scala
classes). The output type of an input supplied to another task should be the
same as the input type, or be in a child class of the input type.

      There exist five types of transitions in OpenMOLE: flat, divergent,
convergent, explorative and aggregative. A flat transition is one in which the output of one
task is the input to a single other task. On the other hand, a divergent
transition is one in which the output of one task serves as the input to several
other tasks. The inverse of a divergent task is a convergent task, in which
several tasks supply input to a single task. Explorative transitions allow for
multiple excutions of the same task on the sampling outputs produced by an
exploration task. Conversly, an aggregative transition gathers all the streams
produced by an explorative transition. It is also possible to add a stopping
condition to terminate all streams once a condition is satisfied.

      Tasks are not directly connected to each other by transitions. They are
encapsulated within \textit{capsules} who are connected to each other by
transitions. This permits the same task to be used multiple times in the
workflow by encapsulating them in different capsules.

    There also exists the notion of \textit{Input Slots} in OpenMOLE, which enables
cycles in the workflow. A task may have several input slots and will execute
each time that all the transitions belonging to the same input slots has passed
through.

        \subsection{Pipeline execution}

      In order for an OpenMOLE workflow to be executed, there must exist a
single encapsulated task. A task will execute once all its dependencies have
been met.

    During execution of a task, the CARETask will decompress the CARE archive
containing the application and its dependencies and the application is deployed
within the confines of the decompressed archive.

OpenMOLE relies on the exit code returned by the application in order to
determine whether to reschedule the task. It is possible to prevent task
rescheduling by setting the boolean flag \textit{errorOnReturnValue} to false.

      OpenMOLE workflows can be executed on a variety of platforms such as
remote servers, clusters and compute grids. As these execution hosts may not have all
the required dependencies to execute a task, tasks are archived using CARE. This
ensures that all the required applications and their dependencies can be shipped
and executed at runtime on any Linux host.

        \subsection{Debugging and Provenance}
    A CARETasks standard output and standard error are normally printed out to
OpenMOLES's console. For distributed executions, this might not be a practical
solution, in which case such information may be passed through
the dataflow using OpenMOLE variables.

    \section{LONI}
    \section{Automatic Analysis}
    \section{Dipy, Make, Pydiper} 
    \section{Use of containers in Workflow engines} 
        \subsection{use of containers in nipype, psom, spm}
